Who does big team science?

### 2023-06-15 manuscript_scopus.Rmd
updated authors

```{r total-authors}
total_authors <- 3047067 # only this updated
#### DAMMIT FORGOT THIS ####
avg_authors <- apa_num(49.904646)
sd_authors <- apa_num(207.006114)
min_authors <- 10
med_authors <- 19
max_authors <- 5155
```

>>>>

```{r total-authors}
total_authors <- 510334 # only this updated
#### DAMMIT FORGOT THIS ####
avg_authors <- apa_num(49.30516877182394)
sd_authors <- apa_num(212.9786134634032)
min_authors <- 10
med_authors <- 18
max_authors <- 5568
```
